DOpElib: A Goal Oriented Software Library for Computing PDEs and Optimization Problems

### 2012-10-05 Paper_May_2012/main.tex
Paper: Im FSI einen Code-Schnipsel hinzugefuegt, der veranschaulicht, wie einfach andere Zeitschrittverfahren ausgewaehlt werden koennen

\todo{In den Beispielen in Pseudo code evtl. zeigen, was der 
Nutzer aendern kann.}

@@

The configuration is 
sketched in Figure \ref{configuration_csm_and_fsi_2D}. Details 
on parameters and evaluation functionals and other results 
can be found in \cite{HrTu06b, BuSc06, TuHrMaRaWoAc10, DeHaeAnnBrVie10, Wi11}. 
The Fractional-Step-$\theta$ scheme is used for time discretization with
different time step sizes $k$. Since the problem is fully nonstationary, the 
dynamics are presents in Figure \ref{res:fsi_2_mesh_and_x_velo}. 
By comparison of our findings in Figure \ref{res:results_ux_and_uy_fsi_2}
with the literature, it can be identified that 
the implementation in DOpElib is correct.

>>>>

@@

The configuration is 
sketched in Figure \ref{configuration_csm_and_fsi_2D}. Details 
on parameters and evaluation functionals and other results 
can be found in \cite{HrTu06b, BuSc06, TuHrMaRaWoAc10, DeHaeAnnBrVie10, Wi11}. 
The Fractional-Step-$\theta$ scheme is used for time discretization with
different time step sizes $k$. However, the time stepping scheme can be 
very easily chosen in the \texttt{main.cc} function by declaring
\begin{lstlisting}
#define TSP1 ForwardEulerProblem
#define TSP2 BackwardEulerProblem
#define TSP3 CrankNicolsonProblem
#define TSP4 ShiftedCrankNicolsonProblem
#define TSP5 FractionalStepThetaProblem
\end{lstlisting}
and then using the designated scheme.

Since the problem is fully nonstationary, the 
dynamics are presents in Figure \ref{res:fsi_2_mesh_and_x_velo}. 
By comparison of our findings in Figure \ref{res:results_ux_and_uy_fsi_2}
with the literature, it can be identified that 
the implementation in DOpElib is correct.
